diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2020-04-06 jss-article-rnw-diffEnrich/article.Rnw
Added parameter description for get_kegg function in app note

@@

<<<get_kegg_read, echo = TRUE>>=
## run get_kegg() using rat
date <- as.character(Sys.Date())
kegg_rno <- get_kegg(read = TRUE,
                     path = here::here(),
                     date = date,
                     release = "92")
@

>>>>

\begin{table}[]
  \centering
  \caption{\label{tab:description} Description of parameter usage for \code{get\textunderscore kegg}.}
  \begin{adjustbox}{width=\textwidth}
  \begin{tabular}{lll}
  \hline
\textbf{Argument} & \textbf{Description}                                                                                                                                                                                                                                     & \textbf{Example}            \\
\hline
species           & \begin{tabular}[c]{@{}l@{}}character. The species to use in kegg  \\ data pull\end{tabular}                                                                                                                                                                                                         & species = 'rno'             \\
read              & \begin{tabular}[c]{@{}l@{}}logical. Should \code{get\textunderscore kegg} read in files from previous call. If TRUE, all 3 files \\ generated by \code{get\textunderscore kegg} must be in the same directory and the user must \\ provide a file path that points to that directory.\end{tabular} & read = TRUE                 \\
path              & \begin{tabular}[c]{@{}l@{}}character. A character string describing the path \\ to write out KEGG API data sets. If not provided, \\ defaults to current working directory.\end{tabular}                                                                 & path = "path/to/directory/" \\
date              & \begin{tabular}[c]{@{}l@{}}character. A character string describing the date that \\ was used to time stamp files from previous call. \\ Must be formatted like YYYY-MM-DD.\end{tabular}                                                                 & date = "2020-04-10"          \\
release           & \begin{tabular}[c]{@{}l@{}}character. A character string describing the KEGG\\  release that was used to time stamp \\ files from previous call (e.g. "90", "92", "94")\end{tabular}                                                                     & release = "92"
\end{tabular}
\end{adjustbox}
\end{table}

@@

<<<get_kegg_read, echo = TRUE>>=
## run get_kegg() using rat
date <- as.character(Sys.Date())
kegg_rno <- get_kegg(read = TRUE,
                     path = here::here(),
                     date = date,
                     release = "94")
@

### 2020-04-06 jss-article-rnw-diffEnrich/article.tex
Added parameter description for get_kegg function in app note

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Kegg Release: Release\_92.0+\_12-05\_Dec\_19}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Kegg Release: Release\_92.0+\_12-05\_Dec\_19}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## run get_kegg() using rat\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
date <- as.character(Sys.Date())\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
kegg_rno <- get_kegg(read = TRUE,
                     path = here::here(),
                     date = date,
                     release = "92")\end{lstlisting}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# ncbi\_to\_kegg2019-12-05Release\_92.0+\_12-05\_Dec\_19.txt}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# kegg\_to\_pathway2019-12-05Release\_92.0+\_12-05\_Dec\_19.txt}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# pathway\_to\_species2019-12-05Release\_92.0+\_12-05\_Dec\_19.txt}}

>>>>

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Kegg Release: Release\_94.0+\_04-06\_Apr\_20}}\end{kframe}
\end{knitrout}

\begin{table}[]
  \centering
  \caption{\label{tab:description} Description of parameter usage for \code{get\textunderscore kegg}.}
  \begin{adjustbox}{width=\textwidth}
  \begin{tabular}{lll}
  \hline
\textbf{Argument} & \textbf{Description}                                                                                                                                                                                                                                     & \textbf{Example}            \\
\hline
species           & \begin{tabular}[c]{@{}l@{}}character. The species to use in kegg  \\ data pull\end{tabular}                                                                                                                                                                                                         & species = 'rno'             \\
read              & \begin{tabular}[c]{@{}l@{}}logical. Should \code{get\textunderscore kegg} read in files from previous call. If TRUE, all 3 files \\ generated by \code{get\textunderscore kegg} must be in the same directory and the user must \\ provide a file path that points to that directory.\end{tabular} & read = TRUE                 \\
path              & \begin{tabular}[c]{@{}l@{}}character. A character string describing the path \\ to write out KEGG API data sets. If not provided, \\ defaults to current working directory.\end{tabular}                                                                 & path = "path/to/directory/" \\
date              & \begin{tabular}[c]{@{}l@{}}character. A character string describing the date that \\ was used to time stamp files from previous call. \\ Must be formatted like YYYY-MM-DD.\end{tabular}                                                                 & date = "2020-04-10"          \\
release           & \begin{tabular}[c]{@{}l@{}}character. A character string describing the KEGG\\  release that was used to time stamp \\ files from previous call (e.g. "90", "92", "94")\end{tabular}                                                                     & release = "92"
\end{tabular}
\end{adjustbox}
\end{table}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Kegg Release: Release\_94.0+\_04-06\_Apr\_20}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
## run get_kegg() using rat\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
date <- as.character(Sys.Date())\end{lstlisting}
\begin{lstlisting}[basicstyle=\ttfamily,breaklines=true]
kegg_rno <- get_kegg(read = TRUE,
                     path = here::here(),
                     date = date,
                     release = "94")\end{lstlisting}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# ncbi\_to\_kegg2020-04-06Release\_94.0+\_04-06\_Apr\_20.txt}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# kegg\_to\_pathway2020-04-06Release\_94.0+\_04-06\_Apr\_20.txt}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# pathway\_to\_species2020-04-06Release\_94.0+\_04-06\_Apr\_20.txt}}
